### 2017-01-10 doc/manuscript.Rmd
Fixed results after HOMA-IR changed to HOMA2

```{r analyze_gee, cache=TRUE}
gee_unadj_df <- analyze_gee(covars = "MonthsFromBaseline")
gee_adj_df <- analyze_gee()
```

@@

`r tab_basic` shows some basic characteristics of the PROMISE cohort. The mean 
follow-up time was `r calc_followup_time()`, where `r calc_pct_full_visits()`%
of participants attended all three visits. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)`. Given the eligibility criteria, the majority of
participants (`r fhd$npct`) had a family history of diabetes.
Between the baseline visit and the 6-year visit in this sample, insulin
sensitivity and beta-cell function measures had a significant median decline
between `r outcome_chg$chg` (p`r outcome_chg$p`; n=`r outcome_chg$n`). There 
were `r dys$dm` and `r dys$pre` incident cases of diabetes and
pre-diabetes (IFG and IGT), respectively. {{ confirm this is incidence }}

`r fig_tagfa` shows the composition of each FA in the TAG fraction (see 
`r stab_tagfa` for raw numerical values of the mean and SD {{ confirm }}). 
Three TAGFA contributed `r format_rounding(sum(tagfa$pct))`% to the total 
TAG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r fig_corr` shows a heatmap of the correlation of individual TAGFA with the
outcome variables and several basic characteristics.
As expected, nearly all TAGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG`) with clinically-measured TAG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist`). There was also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(1/HOMA-IR: r=`r fa_cor$rng['1/HOMA-IR']`, ISI: r=`r fa_cor$rng$ISI`) than 
for the beta-cell function measures (all r<0.30).

@@

As a concentration, nearly all TAGFA had a strong negative association on
1/HOMA-IR {{ change to HOMA2-IS }} and ISI (estimates ranging from 
`r est1$outcome_b$rng[3]` and `r est1$outcome_b$rng[7]`, respectively), and a
few had strong negative associations with IGI/IR and ISSI-2 (estimates ranging 
from `r est1$outcome_b$rng[10]` and `r est1$outcome_b$rng[13]`, respectively).
As a mol%, four TAGFA (14:0, 16:0, 14:1n-7, and 16:1n-7) had negative
associations with 1/HOMA-IR and ISI (between `r est1$outcome_b$rng[1]` and 
`r est1$outcome_b$rng[5]`%, respectively, lower insulin sensitivity for every SD
increase in the TAGFA), while several more TAGFA had positive associations with
1/HOMA-IR and ISI (20:0, 18:1n-9, 20:1n-9, 22:1n-9, 18:2n-6, 20:2n-6, 20:4n-6,
and 22:5n-3) predicting between `r est1$outcome_b$rng[2]` and 
`r est1$outcome_b$rng[6]`%, respectively, higher insulin sensitivity for every
SD increase in the TAGFA. One TAGFA, 20:2n-6, had a very strong positive
association with the insulin sensitivity measures, with a `r est1$b_ci$est[1]`
to `r est1$b_ci$est[36]`% higher insulin sensitivity for every SD increase in 
20:2n-6.

@@

The PLS results for the insulin sensitivity (`r fig_pls`) revealed a clustering 
of the FA 14:0, 14:1n-7, 16:0, and 16:1n-7. These TAGFA loaded strongly (meaning
the FA fell between the dashed and solid circles) and negatively on 1/HOMA-IR
and ISI, suggesting this cluster of TAGFA tracks together with lower insulin
sensitivity. The TAGFA 20:2n-6, 20:5n-3, 22:5n-3, and 22:6n-3 loaded positively
on both insulin sensitivity measures. No other TAGFA loaded strongly, the
results of which remained after running the PLS model on the cross-validated
testing set. The predictive ability of the PLS model, determined by correlating
the predicted outcome values with the actual values, were good (1/HOMA-IR: 
`r cor_pls_homa2$r_p`; ISI: `r cor_pls_isi$r_p`).

>>>>

```{r analyze_gee, cache=TRUE}
gee_unadj_df <- analyze_gee(covars = "YearsFromBaseline")
gee_adj_df <- analyze_gee()
```

@@

`r tab_basic` shows some basic characteristics of the PROMISE cohort. The mean 
follow-up time was `r calc_followup_time()`, where `r calc_pct_full_visits()`%
of participants attended all three visits. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)`. Given the eligibility criteria, the majority of
participants (`r fhd$npct`) had a family history of diabetes.
Between the baseline visit and the 6-year visit in this sample, insulin
sensitivity and beta-cell function measures had a significant median decline
between `r outcome_chg$chg` (p`r outcome_chg$p` from GEE; n=`r outcome_chg$n`). There 
were `r dys$dm` and `r dys$pre` incident cases of diabetes and
pre-diabetes (IFG and IGT), respectively.

`r fig_tagfa` shows the composition of each FA in the TAG fraction (see 
`r stab_tagfa` for raw numerical values of the mean and SD {{ confirm }}). 
Three TAGFA contributed `r format_rounding(sum(tagfa$pct))`% to the total 
TAG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r fig_corr` shows a heatmap of the correlation of individual TAGFA with the
outcome variables and several basic characteristics.
As expected, nearly all TAGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG`) with clinically-measured TAG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist`). There was also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(1/HOMA-IR: r=`r fa_cor$rng['HOMA2-%S']`, ISI: r=`r fa_cor$rng$ISI`) than 
for the beta-cell function measures (all r<0.30).

@@

As a concentration, nearly all TAGFA had a strong negative association on
HOMA2-%S and ISI (estimates ranging from 
`r est1$outcome_b$rng[3]` and `r est1$outcome_b$rng[7]`, respectively), and a
few had strong negative associations with IGI/IR and ISSI-2 (estimates ranging 
from `r est1$outcome_b$rng[11]` and `r est1$outcome_b$rng[15]`, respectively).
As a mol%, four TAGFA (14:0, 16:0, 14:1n-7, and 16:1n-7) had negative
associations with HOMA2-%S and ISI (between `r est1$outcome_b$rng[1]` and 
`r est1$outcome_b$rng[5]`%, respectively, lower insulin sensitivity for every SD
increase in the TAGFA), while several more TAGFA had positive associations with
HOMA2-%S and ISI (20:0, 18:1n-9, 20:1n-9, 22:1n-9, 18:2n-6, 20:2n-6, 20:4n-6,
and 22:5n-3) predicting between `r est1$outcome_b$rng[2]` and 
`r est1$outcome_b$rng[6]`%, respectively, higher insulin sensitivity for every
SD increase in the TAGFA. One TAGFA, 20:2n-6, had a very strong positive
association with the insulin sensitivity measures, with a `r est1$b_ci$est[1]`
to `r est1$b_ci$est[36]`% higher insulin sensitivity for every SD increase in 
20:2n-6.

@@

The PLS results for the insulin sensitivity (`r fig_pls`) revealed a clustering 
of the FA 14:0, 14:1n-7, 16:0, and 16:1n-7. These TAGFA loaded strongly (meaning
the FA fell between the dashed and solid circles) and negatively on HOMA2-%S
and ISI, suggesting this cluster of TAGFA tracks together with lower insulin
sensitivity. The TAGFA 20:2n-6, 20:5n-3, 22:5n-3, and 22:6n-3 loaded positively
on both insulin sensitivity measures. No other TAGFA loaded strongly, the
results of which remained after running the PLS model on the cross-validated
testing set. The predictive ability of the PLS model, determined by correlating
the predicted outcome values with the actual values, were good (HOMA2-%S: 
`r cor_pls_homa2$r_p`; ISI: `r cor_pls_isi$r_p`).
